Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-17 revision-1/hyper.tex
checkpoint

@@

@@

\begin{definition}
  A protocol $\prog$ with $\iov(\prog) = (S,M)$ has \emph{integrity} iff 
  $\forall \adversary . \runs_\adversary(\prog) \subseteq \runs(\prog)$.
\end{definition}

\begin{definition}
  A protocol $\prog$ with $\iov(\prog) = (S,M)$ is \emph{malicious correct} iff:
  $$
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(\{ \outv \}|\store)) =
    \support(\progtt(\prog,\adversary)(\{ \outv \}|\store))
  $$
\end{definition}

@@

>>>>

\subsection{Passive Security and Noninterference}

\cnote{Fix the $O$ output variable things, and scoping of $H,C$.}

@@

\subsection{Gradual Release as a Design Pattern}

\begin{definition}
  Given $H,C$, a protocol $\prog$ with $\iov(\prog) = (S,M,O)$ satisfies \emph{gradual release} iff
  $\sep{\progtt(\prog)}{M_C}{S_H}$.
\end{definition}

\begin{theorem}
  Gradual release implies passive security.
\end{theorem}

\subsection{Malicious Security and Robust Declassification}

@@

\begin{definition}
  A protocol $\prog$ with has \emph{integrity} iff 
  $\forall \adversary . \runs_\adversary(\prog) \subseteq \runs(\prog)$.
\end{definition}

\begin{definition}
  A protocol $\prog$ with $\iov(\prog) = (S,M,O)$ is \emph{malicious correct} iff:
  $$
  \forall \adversary, \store \in \mems(S_H) \ .\ \support(\progtt(\prog)(O_H|\store)) =
    \support(\progtt(\prog,\adversary)(O_H|\store))
  $$
\end{definition}

@@

\begin{definition}[Robust Declassification]
  A protocol satisfies \emph{robust declassification} iff it has integrity and
  satisfies gradual release. 
\end{definition}

\begin{theorem}
  Robust declassification implies malicious security.
\end{theorem}
